---
title: "txomics development"
author: "Lucio Rezende Queiroz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
md_document:
    variant: markdown_github
---

# Before starting

* Install devtools package using:
`install.packages("devtools")`
* Create package folder: `devtools::create("txomics")`


# Adding dependencies
```{r, eval = FALSE}
## CRAN packages
devtools::use_package("tidyr")
devtools::use_package("dplyr")
devtools::use_package("stringr")
devtools::use_package("readxl")
devtools::use_package("readr")
devtools::use_package("jsonlite")
devtools::use_package("purrr")
devtools::use_package("ggplot2")
devtools::use_package("ggrepel")
devtools::use_package("ggpubr")

## Bioconductor packages
devtools::use_package("tximport")
devtools::use_package("DESeq2")
devtools::use_package("fgsea")
```

Edit devtools options for adding metadata to package

```{r, eval = FALSE}
getOption("devtools")
getOption("devtools.path")
getOption("devtools.name")
getOption("devtools.desc.author")
getOption("devtools.desc.license")

options("devtools.name" = "Lucio Rezende Queiroz",
        "devtools.desc.author" = 'person("Lucio", "Rezende Queiroz", 
                                    email = "luciorqueiroz@gmail.com",
                                    role = c("aut", "cre"))')
```

# Adding documentation

Edit function files using `#'` followed by `@tag_name detail` to add documentation
example:
```{}
#' Add together two numbers.
#' 
#' @param x A number.
#' @param y A number.
#' @return The sum of \code{x} and \code{y}.
#' @examples
#' add(1, 1)
#' add(10, 1)
add <- function(x, y) {
  x + y
}
```


use `devtools::document()` to automatic generate the man folder and Rd files for each function
```{r, eval = FALSE}
## rstudio ctrl/cmd + shift + D
devtools::document()
```

# Installing

Running `load_all()` simulates what happen when installing your package
```{r, eval = FALSE}
devtools::load_all()
```


# Create a README file

```{r, eval = FALSE}
devtools::use_readme_rmd()
```


# CRAN check

Use `check()` to  check if the package is suitable for CRAN submission
```{r, eval = FALSE}
devtools::check(document = FALSE)
```

# Appendix

## Licensing

For this package I will be using the MIT license
```{r, eval = FALSE}
devtools::use_mit_license()
```


## Version numbers

The version numbers used in txomics follow the x.y.z model where x is the major version, y is the minor version and is the patch number

Odd minor version are development versions (e.g.: 1.11.0) and even minor version are release candidates (e.g.: 1.12.0).

Patch number version is increased for every commit or merge to development branch (e.g.: from 1.11.1 to 1.11.2)

