---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# txomics <img src="man/figures/txomics_logo.svg" align="right" height=140 />

[![Travis build status](https://travis-ci.com/luciorq/txomics.svg?branch=master)](https://travis-ci.com/luciorq/txomics)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/luciorq/txomics?branch=master&svg=true)](https://ci.appveyor.com/project/luciorq/txomics)
<!-- [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/r-lib/pkgdown?branch=master&svg=true)](https://ci.appveyor.com/project/r-lib/pkgdown) -->
<!-- [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing) -->
<!-- [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active) -->
<!-- [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/pkgdown)](https://cran.r-project.org/package=pkgdown) -->
<!-- [![Coverage Status](https://img.shields.io/codecov/c/github/r-lib/pkgdown/master.svg)](https://codecov.io/github/r-lib/pkgdown?branch=master) -->
[![CRAN status](https://www.r-pkg.org/badges/version/txomics)](https://cran.r-project.org/package=txomics)
[![Coverage status](https://codecov.io/gh/luciorq/txomics/branch/master/graph/badge.svg)](https://codecov.io/github/luciorq/txomics?branch=master)

## Overview

Functional Analysis and Visualization of Transcriptomic Data

## Installation
<!--
When available you will be able to install the released version of txomics from [CRAN](https://CRAN.R-project.org) with:

``` r
## Not available yet
## install.packages("txomics")
```

And the development version from [GitHub](https://github.com/) with:
-->
The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("luciorq/txomics")
```

## Analysis conventions

* A `tibble` data frame is the major data structure that is used, allowing easy customization.
* `txomics` is pipe-friendly and re-exports `%>%` for use. 

<!--
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
-->
---
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
