---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# txomics <img src="man/figures/txomics_logo.svg" align="right" height=140 />

[![Travis build status](https://travis-ci.com/luciorq/txomics.svg?branch=master)](https://travis-ci.com/luciorq/txomics)

## Overview

Functional Analysis and Visualization of Transcriptomic Data

## Installation
<!--
When available you will be able to install the released version of txomics from [CRAN](https://CRAN.R-project.org) with:

``` r
## Not available yet
## install.packages("txomics")
```

And the development version from [GitHub](https://github.com/) with:
-->
The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("luciorq/txomics")
```

## Analysis conventions

* A `tibble` data frame is the major data structure to use.
* `txomics` is pipe-friendly and re-exports `%>%` for use. 

<!--
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
-->
---
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
